%-------------------------
% Resume in Latex
% Author : Ethan Rohman
% Adapted from: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://rohman.com}{\Large Ethan Rohman}} & Email : \href{mailto:ethanmrohman}{ethanmrohman@gmail.com}\\
  \href{http://rohman.com/}{http://www.rohman.com} & Mobile : +1-507-676-5914 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Drake University}{}
      {Bachelor of Science in Computer Science;  GPA: 3.85}{Aug. 2020 -- May. 2024}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Surest}{Minneapolis, MN}
      {Data Science Intern}{May 2022 - May 2024}
      \resumeItemListStart
        \resumeItem{Data Analysis}
          {Conducted a comprehensive analysis of text message campaigns to assess engagement increases, utilizing Python, Pandas, and SQL for data manipulation and analysis.}
        \resumeItem{Machine Learning}
          {Developed a question-answer bot using sentence transformers and built a vector store with a custom embedding model for enhancing search capabilities, managed deployment with MLflow, and fine-tuned chat models for suggesting answers to partial questions.}
        \resumeItem{Search Engine Improvement}
          {Worked on enhancing the search engine using embedding models, including building a custom vector store for improved search results and user experience.}
        \resumeItem{Data Engineering}
          {Executed complex SQL queries with pyspark in Databricks  and contributed to data pipelines using Ascend, demonstrating proficiency in data engineering tasks. Employed PySpark for data processing and automation within Ascend pipelines, and utilized Boto3 for managing AWS S3 data storage solutions.}
        \resumeItem{Presentations}
          {Formally presented findings and projects to groups as large as 40, demonstrating strong communication skills and the ability to translate complex technical details into business insights.}
        \resumeItem{Agile Methodologies}
          {Experienced in Agile development methodologies, actively participating in sprints, managing stories in Jira, and utilizing Notion for project documentation and collaboration.}
      \resumeItemListEnd

    \resumeSubheading
      {Group Senior Project}{Drake University}
      {repo: }{Current}
      \resumeItemListStart
        \resumeItem{Finance Web Application}
          {Collaborating on a finance web application using a PostgreSQL, Django, and Next.js tech stack, focusing on developing robust backend and frontend components as part of a team project.}
          {Utilized Jira for sprint planning and tracking, and Lucidchart for workflow diagrams.}
      \resumeItemListEnd
      
    \resumeSubheading
      {Individual Senior Project}{Drake University}
      {repo: }{Current}
      \resumeItemListStart
        \resumeItem{UI/UX Study}
          {Conducting a UI/UX study as a solo project, using three web applications (calculator, form submission, informational document) to test various UI/UX components and identify combinations that enhance user experience through methodical testing and analysis.}
          {Used Figma for UI/UX design mockups and for prototype testing.}
      \resumeItemListEnd


  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Question Answering Bot}
      {Built a deterministic outcome question-answering bot using sentence transformers, enhancing customer support operations.}
    \resumeSubItem{Text Message Campaign Analysis}
      {Analyzed text message campaigns for a health insurance company to determine engagement increases, using data science techniques.}
  \resumeSubHeadingListEnd

%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
 \resumeSubHeadingListStart
   \item{
     \textbf{Languages}{: Python, SQL, Javascript, HTML, CSS}
   }
   \item{
     \textbf{Technologies/Tools}{: Pandas, PySpark, MLflow, Elasticsearch, Boto3, Docker, Django, PostgreSQL, Next.js, AWS, Notion, Jira,           Lucidchart, Figma, Databricks, Ascend}
   }
 \resumeSubHeadingListEnd

%--------RELATED COURSEWORK------------

\section{Related Coursework}
  \resumeSubHeadingListStart
    \resumeSubItem{Machine Learning}
      {Explored development of programs that learn from data, covering key algorithms and techniques in machine learning. Topics included CNNs, Random Forests, PCA, instance-based learning, Bayesian methods, and NLP.}
    \resumeSubItem{Cloud and Database Systems}
      {Covered virtualization, Python programming, the Hadoop ecosystem, and comprehensive use of Amazon Web Services. Also included database querying techniques with both SQL and NoSQL databases.}
    \resumeSubItem{Advanced Linear Algebra}
      {Studied advanced concepts in linear algebra, underpinning many machine learning and data analysis algorithms.}
  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}

